Seagrass mapping and monitoring \\ along the coasts of Crete, Greece

### 2011-02-06 MScDiplom_Lemenkova.tex
Comment 14 of Valentijn: Fig.4.5: variable iterated over: depth

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.45]{Sensors.png}
	\caption{Combined plots of simulated remote sensing reflectance of \textit{P.oceanica} at various sensors: MODIS, MERIS, SeaWiFS and CZCS.}
	\label{fig:4.6}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.45]{Sensors.png}
	\caption{Combined plots of simulated remote sensing reflectance of \textit{P.oceanica} at various sensors: MODIS, MERIS, SeaWiFS and CZCS, iterated over three depths.}
	\label{fig:4.6}
\end{wrapfigure}
